% name-and-address.tex should just contain plain text with name and address
\topHeading{\input{name-and-address.tex}}

\firstLine{Date of Birth: 1 April 1966}{\jobType}

\sectionHeading{Profile}

I've been using PHP for almost as long as it's existed
and have carried my OOP skills over from nearly 30 years
of use in other languages.
In the last few years moving from plain PHP to MVC frameworks
like Symfony, YII, Laravel
\ifnum\areEqual{\jobType}{Ruby}
and \textbf{Ruby on Rails}.
\else
(and Ruby on Rails).
\fi

I can write complex, optimised and readable SQL queries
as well as using the ORMs included in many frameworks.

\ifnum\areEqual{\jobType}{PHP}
    My strengths certainly lie on the server side
    but I am also quite capable with browser side
    technologies like HTML, CSS, JS, and AJAX.
    And with the HTTP protocol that ties the two sides together.
\fi

\ifnum\areEqual{\jobType}{JS}
    I've been using JavaScript more and more since Douglas Crockford
    showed me it's real power and have been incorporating more of it
    into server-side projects as well as just using it in the browser.
\fi

\ifnum\areEqual{\jobType}{Ruby}
    Due to job availability, I have done far more of my server-side work
    using PHP but Ruby remains my preferred language
    and Rails my preferred framework.
    As well as using Rails when working at Oxford University,
    I also spent my time at Inzent using YII (a "port" of Rails for PHP).
\fi

\ifnum\areEqual{\jobType}{Admin}
    Having been on both the technical and administrative sides on
    "the information business" for 35-odd years,
    I am able to bring my previous experience to bear and to adapt
    to new systems and methodologies.
    Whilst aiming to complete tasks in a timely manner,
    I always try to focus on clarity,
    being aware that others are going to build on my work
    and are going to need to understand what I've done
    without that being a task within itself.
\else
    I've not got a degree but I feel that my 35-odd years of
    experience in a wide range of roles more than makes up for this.
\fi

\sectionHeading{Employment}

\jobHeading
    {Looking for a new role}
    {August 2020 - November 2020}

Whilst being "between jobs", I've been engaged in CPD projects centred around
getting better experience of Docker, Jest, Vue, Laravel and OAuth2.

\jobHeading
    {OSX Limited (Full Stack Developer)}
    {March 2015 - 8 August 2020}

Various development and maintenance tasks including:
\begin{itemize}
    \item A system to handle the complete workflow for a company sourcing accommodation for insurance claimants together with a responsive customer portal.
    \item Custom content management systems for customer websites with portals to handle appointments, quotations, and payments and maintenance of content for same.
    \item A system to handle the workflow for cardiology research.
    \item A system to "intelligently" create rotas for a care-provider agency.
    \item A system to allow searching facilities for national and local government based contract proposals.
\end{itemize}

Client-server architectures with both
internal (JSON) and external (JSON and XML) RESTful APIs.

Documentation using Confluence. Issue handling and breaking down
of customer requirements using Jira. Version control using Git/Bitbucket.

Handling of user documentation and data in Word, Excel and PDF formats.

% !!!!! Low level Doctrine and Symfony Handlers !!!!!

\ifnum\areEqual{\jobType}{JS}
    OSX viewed JS as mostly a browser side technology
    but I was keen to make more uses of it on the server side as well.
    We used Grunt and Webpack to bundle our project assets.
    My main project included a websockets client and server
    for keeping track of which users were currently logged in
    and also included an end-to-end test suite
    using the TestCafe framework.
\else
    Using mainly PHP/Symfony but with other front and back end tools:
    MySQL, NodeJS, Test Cafe, Bootstrap, Less and Sass,
    Polymer web components, JQuery, Grunt, Webpack, Composer,
    Doctrine, Optaplanner, Docker.
    Website security auditing using OWASP's Zed Attack Proxy.
\fi

\jobHeading
    {Oxford University Ecosystem Laboratory (Short Term Contract)}
    {January - February 20151}

Developing a \boldIf{\jobType}{Ruby}{Ruby on Rails}
system to import spreadsheets into a PostgreSQL database.
Documentation and further development of the database.
Using rspec for unit testing / test driven development.

\jobHeading
    {Inzent Limited (Developer)}
    {June - September 2014}

Developing an existing PHP/YII back-end to an
E. commerce system connecting to a PHP/Laravel front-end using JSON.
MySQL, SQLite, and Memcache, SOAP and REST querying affiliate APIs,
responding to REST queries from the front-end.
Improving the search back-end using ElasticSearch.
Android development for a proof-of-concept mobile app.
Git and Bitbucket version control.

\jobHeading
    {Mathembedded Limited, Bristol (Web Developer / Systems Administrator)}
    {November 2011 - March 2014}

Part of a team, developing the PHP/JQuery AJAX UI
for a testing application with PDF report generation,
design of a very large MySQL database
and construction of complex optimised SQL queries.
Creation of \boldIf{\jobType}{Ruby}{Ruby} scripts
to parse SQL queries for insertion into the database.
Devops with Bamboo CI server.
Technical and user documentation in Confluence.
Security testing using Zed Attack Proxy.
Working with the project manager in an Agile/Scrum environment
using git and Stash version control and Jira issue tracking.
Also acting in something of a mentoring role
because of my central role of integrating the UI,
database and lower-level C code.

PHP/JQuery Set-top box streaming video demo for
The International Broadcasting Convention.

Maintenance of IT infrastructure:
configuration of Cent-OS for internal application hosting,
reverse proxying, wildcard SSL certificates
and upkeep of the Joomla website
and previously mentioned web-applications.

\jobHeading
    {Augustus Marketing (Web Development Contract)}
    {March - June 2011}

Creating HTML and CSS from provided assets,
developing PHP for site frameworks and E. commerce,
integrating managed content into Flash.
Wordpress integration.
SOAP and REST APIs.
Video production and photography.

\jobHeading
    {Andy Preston Consultancy / Edge Effect (Self Employed Sole Trader)}
    {2001 - 2011}

Web sites, frameworks and CMSs, Interactive, E. commerce and
data gathering sites with PHP and some Python, XML and JQuery.
Using YouTube, Picasa, and Blogger APIs.
Development of multi-media systems, production of audiovisual
material\ifnum\areEqual{\jobType}{Python}
    (with scripting done with The Python Imaging Library)
\fi.

Simple electronics systems for integration into
sculptures and art installations.

Business admin, accounts, invoicing, preparation of
marketing materials, etc.

I also contributed to and, later, led development
of SpiralSynthModular an Open Source audio processing application,
using C++.

\jobHeading
    {Artsite Limited (Financial Director, IT / Event Organiser)}
    {2008 - 2011}

Maintaining the website; IT procedures; graphic design; event coordination;
production of video for conferences, presentations and the BBC Big Screen.

Preparing memorandum and articles of association;
liaison with bank, Companies House, HMRC and Charities Commission;
accounting procedures; and determining legal requirements.

\jobHeading
    {Apollo Developments (Self Employed Sole Trader)}
    {1996 - 2001}

Developing Windows software using Delphi:
order-processing, a printer driver, multimedia, staff development.

\jobHeading
    {Atek Trading Limited (Visual Basic Programmer)}
    {1995}

Although I was employed as a programmer,
I actually spent my time building and integrating PCs.

\jobHeading
    {Total Mailing Services (Data Conversion Programmer)}
    {1994}

Developing one-off programs converting data to a suitable format for printing.

\jobHeading
    {British Rail South Western Region (General Admin)}
    {1994}

Transferring costing information to Excel - data entry and VBA programming.

\jobHeading
    {(Self Employed Sole Trader)}
    {1992 - 1993}

Developing a graphic library for Clipper in C
with transparent access to different screen resolutions.

\jobHeading
    {Kode Computers Limited - Service Division (Programmer)}
    {1990 - 1992}

Developing extensions to service management
and stock control system using
Sculptor 4GL (an "old school" DSL) on Unix,
automation for BOS accounts,
diagnostic software,
systems admin and procedures.

\jobHeading
    {Kode Computers Limited - Systems Division (Programmer)}
    {1989 - 1990}

Developing reports on BOS accounting / SOP system
using a query based report generator. General systems admin.

\jobHeading
    {New Careers Training (DTP Operator)}
    {1988 - 1989}

Preparing course notes and other documents
using a word processor and Ventura Publisher.

\jobHeading
    {Temple Records Limited ("Computer Wizz Kid")}
    {1987 - 1988}

Maintaining an obsolete CP/M machine and administering a mailing database.

\jobHeading
    {Pentagram Software (Self employed partnership)}
    {1986 - 1987}

Creating presentation software on the BBC Micro and Amiga
using teletext and graphics.

\jobHeading
    {Swindon Sewage Treatment Works (Programmer)}
    {1985 - 1986}

Developing software for process control and scientific data management
on BBC Microcomputers.

\sectionHeading{Education}

\subHeading{Hreod Burna Secondary School, Swindon}

\begin{description}
    \item[1982] 'O' Level: Biology - B
    \item[1982] CSE: Computer Studies - 1, Mathematics - 2,
        Chemistry - 2, Electronics - 3
    \item[1983] 'O' Level: English Language - C, Sociology - C
    \item[1983] CSE: Geology - 2, English Language - 1
    \item[1983] CEE: English and Business Communications - III
\end{description}

\subHeading{The College, Swindon}

\begin{description}
    \item[1986] B/TEC Diploma: Computer Studies - Distinction
\end{description}

\sectionHeading{Spare Time Activities}

Weekends find me either making electronic music videos
or out in the shed tinkering with metalwork and electronics.
Some of my hobby projects are hosted on Gitlab.

\sectionHeading{References}

% Just include the names and addresses of referees in plain text
% in references.tex
\input {references.tex}
